Source Summaries

### 2020-02-03 sourceSummaries.tex
I hope this works

@@

@@

>>>>

\noindent
\subsection{Group member}
Joshua Niemann
\subsection{Citation}

@@

\noindent
Game Theory is the primary theory being tested in this article.  The authors examine various versions of the Bluetooth protocol to determine which versions have the best security measures in place.  In addition, the authors analyze BLE devices in an effort to learn which devices and device manufacturers have the best security.

@@

\noindent
\section{Security Vulnerabilities in Bluetooth Technology as used in IoT}

\Urlmuskip=0mu plus 1mu\relax
\bibentry{lonzetta2018security}

\noindent
This study is about understanding Bluetooth and Iot(Internet of Things) devices. They go in depth on the importance of understanding Bluetooth, the differet attacks possible against Bluetooth and IoT devices, and how to mitigate these attacks using different tequniques.

\noindent
Game Theory is the primary theory being used in this article.  The authors gathered information about many vulnerabilities and exploits in Bluetooth/Iot and determined different mitigation tequniques for each of them.

\noindent
The researchers explained the inner workings of IoT and Bluetooth and then gathered different information on attacks to Bluetooth and Iot. Then, by using the information they found they determined different risk mitigation tequniques for users of Bluetooth and IoT devices.

\noindent
The authors presented multiple vulnerabilities and attacks against Bluetooth and IoT and risk mitigations to combat them, the most notable of them being more awareness from the user's perspective on security issue with bluetooth. The main attacks showcased here are PIN Cracking, Man-in-the-M(MITM), BlueJacking, BlueBorne, Fuzzing, Reflection/Relay, Backdoor, Denial of Service(DOS). Many more attacks are mention as well.

\noindent
Can the analysis tequniques use here be used for any other wireless standard? Could there be an attack on BLE that has to do with power consumtion? What methods can we use to more properly inform users of the risks of IoT and Bluetooth so that they may mitigate said risks?
